Timely Object Recognition

### 2012-06-01 writeups/nips12/introduction.tex
edits of abstract, intro, related work
some squeezing

new "myparagraph" environment which is more space economic

The computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
However, in most real-world applications of object recogniition, performance is time-sensitive and inherently tied to the many-class nature of the world.

>>>>

The computer vision field has converged on a general method for object detection, and a standard evaluation of results.
Efficiency is not a concern of the evaluation metrics, and the methods are not evaluated in an inherently multi-class setting.
However, in most real-world applications of object recognition, performance is time-sensitive and inherently tied to the many-class nature of the world.

### 2012-06-01 writeups/nips12/nips2012.tex
edits of abstract, intro, related work
some squeezing

new "myparagraph" environment which is more space economic

@@

\begin{abstract}
In a large visual multi-class detection framework, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation.
\end{abstract}

>>>>

\newcommand{\myparagraph}[1]{\vspace{-0.1cm}{\bf #1}}

@@

\begin{abstract}
In a large visual multi-class detection framework, the problem of timeliness of results is crucial.
We are motivated by situations where running all detectors would take an unacceptably long time, and the best answer must be given by some deadline.
Our method for multi-class detection aims to give the best possible performance at any single point after a start time; it is terminated at a deadline time.
Toward this goal, we formulate a dynamic, \emph{closed-loop} policy guided by inference of the contents of the image in order to decide which detector to deploy next.
In contrast to previous work, our method significantly diverts from the predominant greedy strategies and therefore learns to employ actions without any immediate reward for the goal of detection.
We evaluate our method with respect to performance in the novel Average Precision (AP) vs. Time evaluation on the widely used PASCAL VOC object detection dataset.
With our method, if execution is stopped when only half the detectors have been run, our method obtains $66\%$ better AP than a random ordering, and $14\%$ better performance than an intelligent baseline.
Overall, our method obtains at least $11\%$ better performance on the AP vs. Time evaluation. At time of publication we will make our code available, which is easily extendible to new detectors, classifiers, tasks and reward functions due to the modular nature of our formulation.
\end{abstract}

### 2012-06-01 writeups/nips12/related.tex
edits of abstract, intro, related work
some squeezing

new "myparagraph" environment which is more space economic

\paragraph{Single-class detection}
The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.

Window proposal is often done exhaustively over the image space, as a ``sliding window''.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.

None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.

\paragraph{Context}
Context has a foundational role in vision.
One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.

@@

\paragraph{Multi-Class Detection}
Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.

\paragraph{Cascades}
An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.

However, cascades are not dynamic policies---they cannot change the order of execution based on observations obtained during execution, which is our goal.

\paragraph{Anytime Algorithms and Active Classification}
Anytime performance in vision systems is a surprisingly little-explored idea.
A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs. time \cite{Vijayanarasimhan2010}.

There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
This line of work is closest to our approach.
Most commonly, the scheduling in these approaches is greedy with respect to some quantity such as expected information gain.

In contrast, we are able to learn policies that take actions without any immediate reward.

>>>>

\myparagraph{Single-class detection}
The best recent performance has come from detectors that use gradient-based features to represent objects as either a collection of local patches or as object-sized windows \cite{Dalal2005,Lowe2004}.
Classifiers are then used to distinguish between featurizations of a given class and all other possible contents of an image window.
%
Window proposal is often done exhaustively over the image space, as a ``sliding window''.
Using ``jump windows'' (window hypotheses voted on by local features) as region proposals is another common idea~\cite{Vedaldi2009,Vijayanarasimhan2011}.
For local feature-based approaches, a bounded search over the space of all possible windows works reasonably well~\cite{Lampert2008a}.
%
None of the best-performing systems treat window proposal and evaluation as a closed-loop system, with feedback from evaluation to proposal.
Some work has been done on this topic, mostly inspired by ideas from biological vision and attention research~\cite{Butko2009,Vogel2008,Paletta2005}.

\myparagraph{Context}
Context has a foundational role in vision.
One source of context is the scene or other non-detector cues; the most common scene-level feature is the GIST \cite{Oliva2001a} of the image.
For the commonly used PASCAL VOC dataset \cite{pascal-voc-2010}, GIST and other sources of context are quantitatively explored in~\cite{Divvala2009}.

@@

\myparagraph{Multi-Class Detection}
Work on inherently multi-class detection focuses largely on making detection time sublinear in the number of classes through sharing features \cite{Torralba2007,Fan2005,Razavi2011}.
A proposed post-processing extension to detection systems uses structured prediction to incorporate multi-class context as a principled replacement for the common post-processing step of non-maximum suppression \cite{Desai2009}.

\myparagraph{Cascades}
An early success in efficient object detection used simple, fast features to build up a \emph{cascade} of classifiers, which then considered image regions in a sliding window regime \cite{Viola2001}.
Although the simple features and classifiers of this method have been surpassed by more complex detectors, the idea of cascading classifier evaluations is still often used.
Most recently, cyclic optimization has been applied to optimize cascades with respect to feature computation cost as well as classifier performance \cite{Chen2012}.
However, cascades are not dynamic policies---they cannot change the order of execution based on observations obtained during execution, which is our goal.

\myparagraph{Anytime Algorithms and Active Classification}
Anytime performance in vision systems is a surprisingly little-explored idea.
A recent application to the problem of visual detection picks features with maximum value of information in a Hough-voting framework, and explicitly evaluates performance vs. time \cite{Vijayanarasimhan2010}. 
There has also been work on active classification \cite{Gao2011} and active sensing \cite{Yu2009}, in which intermediate results are considered in order to decide on the next classification step.
This line of work is closest to our approach.
Most commonly, the scheduling in these approaches is greedy with respect to some quantity such as expected information gain.
In contrast, we are able to learn policies that take actions without any immediate reward.
